%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {Foxconn Technology Group} % Organization
    {Kaohsiung, Taiwan} % Location
    {Aug. 2019 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, developed and deployed the overall asynchronous architecture in pcb printer parameter system via Python, Celery, RabbitMQ, Docker, Supervisor, PostgreSQL.}
        \item {Design and developed the overall backend analytical job architecture and RESTful API services with Docker-Compose, RabbitMQ, Flask, PostgreSQL in panel data analysis system.}
        \item {Refactored the code of Blind-Search service to improve reusability and flexibility in panel data analysis system.}
        \item {Built fully automated CI/CD pipelines via Drone CI, Gitlab for data platform project with docker-compose.}
        \item {Surveyed massive big data tech stacks, implemented and deployed CDH infrastructure including HDFS, Spark, Kafka, Impala, Kudu, Zookeeper.}
        \item {Designed the overall tech architecture and leveraged suitable tech stack in data platform project.}
        \item {Implemented core pipeline running sort algorithm with Python, MongoDB in data platform project.}
        \item {Designed and developed many RESTful APIs via FastAPI, Uvicorn, Gunicorn, also designed schema for MongoDB in data platform project.}
        \item {Actively attended internal tech sharing to give talks, talked about clean code guide, virtual environment and package management experience in Python.}
        \item {Actively involved to set up Python coding style guide reference Google style guide.}
        \item {Wrote the SQL commands for web team to integrate the API.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {Pi Software Corp.} % Organization
    {Kaohsiung, Taiwan} % Location
    {Mar. 2017 - July. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built and developed streaming and batch data pipeline of https://zi.media (Alexa Taiwan top 50 site) via Python, Kafka, MongoDB, Redis, Memcached, Elasticsearch.}
        \item {Developed and deployed RESTful APIs to handle article data(daily request around 1 million times) in zi.media with Nginx, Uwsgi, Flask, Redis, MongoDB.}
        \item {Designed and developed NLP services and web api including article keyword extraction(tf-idf), content based recommendations(cosine-similarity), text classification(fasttext), topic model (LDA).}
        \item {Developed and maintained more than 50 web crawlers and optimized the company’s internal distributed crawler system with Kafka, Scrapy, Redis and OrangePi.}
        \item {Developed and deployed ETL system to process company and interview data with calculating ranking score for website (https://interview.tw), and use the RFM model to improve the popular ranking algorithm with Elasticsearch and MongoDB.}
        \item {Developed and deployed salary data analysis report with ETL job for website (https://salary.tw) with Pandas, MongoDB, Numpy.}
        \item {Developed and deployed finance data ETL system and stock news robot for website (https://www.moneybar.com.tw/).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Procurement Specialist} % Job title
    {Taiwan Hopax Chemicals. Mfg. Co., Ltd.} % Organization
    {Kaohsiung, Taiwan} % Location
    {July. 2014 - Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responsible for the company's major chemical raw materials sourcing.}
        \item {Responsible for cost reduction and supplier management.}
        \item {Developed the price prediction model of styrene and acrylic acid, using R language.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Research assistant} % Job title
  %   {National Chung Hsing University} % Organization
  %   {Taichung, Taiwan} % Location
  %   {Sep. 2012 - Jun. 2013} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {International journals researching the field of game theory.}
  %       \item {Assist in writing the National Science Council research plan.}
  %       \item {Write the game model code in Mathematica.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
